A comparison of classification algorithms applied to the Adult Database

### 2009-12-09 report/final.tex
initial description of cn2 experimental results.

>>>>

The CN2 software used supports different algorithms for building either ordered
or unordered rule sets and with different error estimations: laplacian, naive,
information gain and modified entropy. We've tested each combination of
parameters and the overall results are presented in table \ref{tbl:results_cn2}.

\begin{table}
\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error Estimate} & \textbf{Train Error Rate} & \textbf{Test Error Rate} & \textbf{Time}
\end{tabular}
\caption{Results for CN2.}
\label{tbl:results_cn2}
\end{center}
\end{table}
